The exponential growth of digital entertainment platforms created new challenges for users who now have to navigate the enormous landscape of available choices. This makes efficient movie recommendation systems more important than ever to help people find movies tailored to their needs and preferences. The available solutions use various techniques to analyze the user-movie interaction, movie features or a combination of both.

Current research focuses on various approaches but the most prominent ones include Collaborative Filtering, Content-based Filtering and Deep Learning based methods.

Collaborative Filtering aims to identify users with similar preferences and makes recommendations based on the instances liked by other people in the same group. Content-based Filtering focuses on the analysis of the movie features (such as genre, actors and directors) and makes use of previous user impressions. Deep Learning approaches leverage various models such as Multilayer Perceptron Networks, Restricted Boltzmann Machines and Autoencoders to create efficient recommendations.

In this paper, we present a Collaborative Filtering system leveraging the K-means clustering algorithm and association rules to predict the rating a given user would give to a specific movie based on the impressions from similar users. We used the Movie-Lens dataset to train and test the model and achieved a significant performance increase (in terms of Mean Absolute Error) compared to less complex approaches based on calculating the mean rating globally, for a specific movie, and a specific user.